A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-10-21 kobakian-cook.Rmd
Zoom in on Figure 5 d

```{r filtergrid, fig.cap = "Each key step in the hexagon allocation process. The full hexagon grid in a) is created first. The buffer is applied and the remaining points are shown as larger, dark green circles, the potential hexagon points that were removed are shown as smaller, light green points. For each centroid in the set, c) shows the points left after the closest points are selected as potential locations. The relationship between Hobart (the cross) and the centroid (the yellow triangle is used to filter the potential locations within a wedge."}
g1 <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) + 
   theme_void() + 
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = grid, size = 1) +
  coord_equal() + ggtitle("a")

@@

g2 <- ggplot() + 
   geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) +  
  theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#55b56c", data = full_grid, size = 0.5) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = grid, size = 1.5) + ggtitle("b")

@@

f1 <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) +
  theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#55b56c", data = grid, size = 0.5) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1.5) + 
  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 24) + 
#Hobart
  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 2, shape = 3) + ggtitle("c")

@@

```{r filterprocess, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, height = 8}
full_grid <- full_grid %>% filter(hex_long > bbox$min[1], hex_long < bbox$max[1],
                                  hex_lat > bbox$min[2], hex_lat < bbox$max[2])

@@

f2 <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) +
  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011)), data = fort_allocated, fill = "#353b38", colour = "black", size = 0.01) +
  #Hobart
  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 2, shape = 3) + 
  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 24) + 
  theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", fill = "white", data = hex, size = 1.5, shape = 21) + ggtitle("d")

gridExtra::grid.arrange(g1, g2,
                        f1, f2)
```

>>>>

```{r filtergrid, fig.cap = "Each key step in the hexagon allocation process. The full hexagon grid in a) is created first. The buffer is applied and the remaining points are shown as larger, dark green circles, the potential hexagon points that were removed are shown as smaller, light green points. For each centroid in the set, c) shows the points left after the closest points are selected as potential locations. The relationship between Hobart (the cross) and the centroid (the yellow triangle is used to filter the potential locations within a wedge."}
g1 <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) + 
   theme_void() + 
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = grid, size = 1) +
  coord_equal()

@@

g2 <- ggplot() + 
   geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) +  
  theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#55b56c", data = full_grid, size = 0.5) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = grid, size = 1)

@@

f1 <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) +
  theme_void() + coord_equal() +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#55b56c", data = grid, size = 0.5) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1) + 
  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 25) + 
#Hobart
  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 2, shape = 4)

@@

```{r filterprocess, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, height = 12}
full_grid <- full_grid %>% filter(hex_long > bbox$min[1], hex_long < bbox$max[1],
                                  hex_lat > bbox$min[2], hex_lat < bbox$max[2])

@@

f2 <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas %>% filter(lat < -40.3), fill = "#D3D3D3", colour = "white", size = 0.01) +
  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011)), data = fort_allocated, fill = "#353b38", colour = "black", size = 0.01) +
  #Hobart
  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 3, shape = 4) + 
  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 25, size = 2) + 
  theme_void() + coord_equal() +
  # possible choices to select
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1.5) +
  # selected hexagon
  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", fill = "#ede187", data = hex, size = 2.5, shape = 21)

# gridExtra::grid.arrange(g1, g2,
#                         f1, f2)

cowplot::plot_grid(g1, g2,
                   f1, f2, labels = c("a", "b", "c", "d"))
```
